### 2018-03-22 0_intro.tex
started Chapter 3 on describing the portability in general and the encoding into SMT.

\chapter{Introduction}
\label{ch:introduction}

@@

One possible approach is to use an efficient implementation of an SMT-solver (a SAT-solver extended by satisfiability modulo theories)~\cite{Porthos17}. % <-- TODO
This approach allows to capture symbolically the semantics of both the program and the weak memory model while encoding it into a single SMT-formula.
Most modern SMT-solvers are efficient enough to be able to operate the state space of size~??? [CITATION-?].

@@

Current thesis aims to improve the proof-of-concept tool \texttt{PORTHOS} firstly introduced in April 2017 in the work~\cite{Porthos17} by extending the input language, which currently represents the minimum subset of C, and revising the general architecture of the tool in order to enhance performance, reliability and mantainability.

\section{Thesis structure}
\label{ch:introduction:structure}

@@

>>>>

\chapter{Introduction}
\label{ch:intro}

@@

%TODO: BMC
One possible approach is to use an efficient implementation of an SMT-solver (a SAT-solver extended by satisfiability modulo theories)~\cite{Porthos17}. % <-- TODO
This approach allows to capture symbolically the semantics of both the program and the weak memory model while encoding it into a single SMT-formula.
Most modern SMT-solvers are efficient enough to be able to operate the state space of size~[CITATION-?].

@@

Current work aims to improve the proof-of-concept tool \texttt{PORTHOS} firstly introduced in April 2017 in the work~\cite{Porthos17} by extending the input language, which currently represents the minimum subset of C, and revising the general architecture of the tool in order to enhance performance, reliability and mantainability.

\section{Thesis structure}
\label{ch:intro:structure}

@@

% TODO: Add intro to the bounded reachability analysis using SAT -- ?

### 2018-03-22 1_wmm.tex
started Chapter 3 on describing the portability in general and the encoding into SMT.

Over the last decades, the problem of formalisation of the weak memory models
%for different software systems and hardware architectures
has been developed significantly. Research of WMM aimes, firstly, to formalise the weak memory models and provide systematic, sound and complete formal approach of defining WMMs in order to be able to verify systems with respect to them. 
//the cat language here.

@@

\section{The event-based program representation}

@@

The event-based program model represents the directed graph (\textit{event-graph}), where vertices represent \textit{events}, and edges represent \textit{relations} over the events. An event is something, that, after being executed, changes the state of an abstract machine executing the concurrent program. 
An \textit{execution} (trace, run) of a given program is an order of events.
%associated with the instructions of the program
%the path in the event-graph. 
An execution is considered to be \textit{valid} if the memory events follow a single global timeline, i.e., can be embedded in a single partial order allowed by the memory model restrictions~\cite{alglave2010shared}. An execution to be checked on validity is called the \textit{candidate execution}.

@@

@@

the CAT language [ref to Jade's paper] (hard part: to decipher the Alglave's paper).

>>>>

%"Semantics and verification under weak memory models have been the subject of study at least since 2007." [PORTHOS]
The \textit{weak memory model} is a set of predicative constraints on possible executions of a concurrent program. The study of formalisation the weak memory models for different architectures is being rapidly developed over last decade. Research of WMM aimes, firstly, to formalise the weak memory models and provide systematic, sound and complete formal approach of defining WMMs in order to be able to verify systems with respect to them.

%The generic framework of program analysis under weak memory models presented in~\ref{alglave2010shared} is discussed in Section~\ref{ch:wmm:event}.

@@

\section{The event-based program representation}
\label{ch:wmm:event}

%"The semantics of a program is a set of executions" https://johnwickerson.github.io/papers/memalloy.pdf

@@

The event-based program model represents the directed graph (\textit{event-graph}), where vertices represent \textit{events}, and edges represent \textit{relations} over the events. An event is something, that, after being executed, changes the state of an abstract machine executing the concurrent program. 
An \textit{execution} (trace, run) of a given program is an ordered set of events.
%associated with the instructions of the program
%the path in the event-graph. 
An execution is considered to be \textit{valid} if the memory events follow a single global timeline, i.e., can be embedded in a single partial order allowed by the memory model restrictions~\cite{alglave2010shared}. An execution to be checked on validity is called the \textit{candidate execution}.

@@

\subsection{Executions}
\label{ch:wmm:model:executions}

The semantics of a concurrent program is represented by the set of allowed executions.
An execution is uniquely defined by the set $\mathbb{X}$ of events have been executed in each thread (the \textit{control-flow} of a program), and the relations $\mathtt{rf}$ and $\mathtt{co}$ (\textit{data-flow} of a program)~\ref{alglave2010shared}. As it was shown in~\ref{wickerson2017automatically}, it is enough for memory models to constrain the executions independently instead of constraining the program as a whole.

@@

The Porthos tool uses the language \texttt{CAT}~\ref{alglave2016syntax} for defining weak memory models.
